Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-12 paper/main.tex
Minor errors

Detecting menus based on pixel difference between frames poses three challenges.  First, compressed 
video contains frame-to-frame noise that clouds the signal of a change in UI appearance, 
particularly if UI widgets tend to fade in or out gradually.  Second, these menus occlude
heterogeneous backgrounds (photos in Photoshop, colorful code in the IDE), making the difference
at each individual pixel highly-varied relative to its neighbors when a new object appears in the
foreground, even if it is of homogeneous color.  Third, depending on the operating system, 
the edges dividing menus from ribbons and borders in the main UI may be subtle compared to the
internal edges in a menu caused by text or internal horizontal lines that separate groups of options.
This makes it impossible to apply traditinoal segmentation techniques to extract menu regions from 
static images.

@@

The quality of our region proposals is promising.  Our technique locates region proposal that
overlapping with the ground truth in 30/33 (91\%) of the test events.  We see an average 
intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
for all menu appearances.  We note that the strength of our technique varies depending
on operating system.  For example, our system produced low-overlap region proposals
on a computer like Windows 2000, where the menu and application background color were likely
indistinguishable to our difference detection methods (Figure~\ref{fig:proposal5}, Figure~\ref{fig:proposal6}).

@@

Our technique shows promise for extracting menu regions from UI videos.  We took preliminary efforts
to determine how to detect frame indexes where menus appear.  We hypothesize that frames with a 
high absolute pixel difference over their predecessors contained UI events.  To test his hypothesis, 
we extracted frames from one tutorial video for which the absolute pixel difference in the last 10
frames was in the 90th percentile of all differences.  Taking a sample of 50 of these frames, we confirmed that
\emph{nearly all} frames in this percentile showed a UI event in progress.  Of these, only 6 (12\%) 
were menu appearances or disappearances.  We conclude that while pixel difference-based inspection of frames may lead to
high precision detection of UI events in general, more specialized techniques are needed to
delineate menu-based UI events from application switches, window repainting, and window
appearances and disappearances in the future.

>>>>

Detecting menus based on pixel difference between frames poses three challenges.  First, compressed 
video contains frame-to-frame noise that clouds the signal of a change in UI appearance, 
particularly if UI widgets tend to fade in or out gradually.  Second, these menus occlude
heterogeneous backgrounds (photos in Photoshop, colorful code in the IDE), making the difference
at each individual pixel highly-varied relative to its neighbors when a new object appears in the
foreground, even if it is of homogeneous color.  Third, depending on the operating system, 
the edges dividing menus from ribbons and borders in the main UI may be subtle compared to the
internal edges in a menu caused by text or internal horizontal lines that separate groups of options.
This makes it impossible to apply traditional segmentation techniques to extract menu regions from 
static images.

@@

The quality of our region proposals is promising.  Our technique locates region proposals that
overlap with the ground truth in 30/33 (91\%) of the test events.  We see an average 
intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
for all menu appearances.  We note that the strength of our technique varies depending
on operating system.  For example, our system produced low-overlap region proposals
on a computer like Windows 2000, where the menu and application background color were likely
indistinguishable to our difference detection methods (Figure~\ref{fig:proposal5}, Figure~\ref{fig:proposal6}).

@@

Our technique shows promise for extracting menu regions from UI videos.  We took preliminary efforts
to determine how to detect frame indexes where menus appear.  We hypothesize that frames with a 
high absolute pixel difference over their predecessors contained UI events.  To test this hypothesis, 
we extracted frames from one tutorial video for which the absolute pixel difference in the last 10
frames was in the 90th percentile of all differences.  Taking a sample of 50 of these frames, we confirmed that
\emph{nearly all} frames in this percentile showed a UI event in progress.  Of these, only 6 (12\%) 
were menu appearances or disappearances.  We conclude that while pixel difference-based inspection of frames may lead to
high precision detection of UI events in general, more specialized techniques are needed to
delineate menu-based UI events from application switches, window repainting, and window
appearances and disappearances in the future.
